Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-15 IEEE_ConferenceOnGames/article_english.tex
Update to article  14/5/2019 17:52

\section{Introduction}
Procedural content generation is an interesting subject on the entertainment
industry, primarily in video game development because of the savings in 
time and human resources when generating content for different video game projects.
In this paper an evolutionary content generation system is proposed to generate
levels for the popular Angry Birds video game \cite{RovioEntertainmentCorporation2009},
taking inspiration in concepts of open-ended evolution. Angry birds is a game 
developed by Rovio Entertainment in which the objective is to destroy structures
placed on the map as well as eliminating
green pig-like entities in order to obtain the highest score possible, the game
uses a gravity and collition system that allows the structures to fall and be
destroyed by means of damage as well as the use of three different construction
materials \textit{ice}, \textit{wood} and \textit{stone} each one with a different
resistance, ranging from fragile, normal and sturdy in that order. The game
mechanic is to use a slingshot to shoot a certain number of birds with different
abilities, to destroy both the structures and the objectives. A high score 
is achived by doing the most destruction with the least birds possible 
\cite{RovioEntertainmentCorporation2009}.

@@

\subsection{Original approach}
% This sentence needs more work -MG
Since the algorithm has to generate more complex structures the remaining pieces
of a member of the population have to be used has a starting point, this new
% we don't use member of the populations, use proposed solution, candidate solution
% or individual of the population. - MG

additions to the piece pool are added to the population by the mutation
operation, the objective in the first phase of the project is to generate
structures that are capable of maintaining their own balance as shown on figure
\ref{test_old}, since the objective of open-ended evolution for this project is
to add new composites to the pool of options the algorithm will first run a
simulation with a group of pieces and after it the ones that were not destroyed
by falling because of gravity will be saved and added to the pool of options.

@@

The way to represent the elements of a member of the population is by using the
id of each piece and the new added ones has a pointer to the respective data
that needs to be obtained, this way and individual can be represented as shown
on figure \ref{old_chrom} where each chromosome represents a certain item in the
pool of pieces, the numbers for this elements are assigned in a first come first
served basis, the numbers are infinitely incremented and the same pieces can be
repeated on each individual of the population.

>>>>

\section{Introduction}
Procedural content generation is an interesting subject on the entertainment
industry, primarily in video game development because of the savings in 
time and human resources when generating content for different video game projects \cite{Yannakakis2017,YannakakisContentGeneration}.
In this paper an evolutionary content generation system is proposed to generate
levels for the popular Angry Birds video game,
taking inspiration in concepts of open-ended evolution. Angry birds is a game 
developed by Rovio Entertainment in which the objective is to destroy structures
placed on the map as well as eliminating
green pig-like entities in order to obtain the highest score possible, the game
uses a gravity and collition system that allows the structures to fall and be
destroyed by means of damage as well as the use of three different construction
materials \textit{ice}, \textit{wood} and \textit{stone} each one with a different
resistance, ranging from fragile, normal and sturdy in that order. The game
mechanic is to use a slingshot to shoot a certain number of birds with different
abilities, to destroy both the structures and the objectives. A high score 
is achived by doing the most destruction with the least birds possible 
\cite{RovioEntertainmentCorporation2009}.

@@

\subsection{Original approach}
% This sentence needs more work -MG
During the original phase of the design of the system, it was decided that the way 
the composites were going to evolve was by first placing only base pieces on a level 
then after a simulation the remaining pieces
of a member of the population were going to be used has a new composite if after a 
simulation a group was still standing and grouped on a single point, their individual 
offsets from the center of the group was calculated and then using this information a new 
composite could be added to the pool of options, this new
% we don't use member of the populations, use proposed solution, candidate solution
% or individual of the population. - MG  
additions to the composite pool could then be added to the population by the mutation
operation when a new member of the population was being created, the objective 
in this first phase of the project was to generate
structures that were capable of maintaining their own balance as shown on figure
\ref{test_old}, since the objective of open-ended evolution for this project is
to add new composites to the pool of options, then the algorithm will first run a
simulation with a group of pieces and after it the ones that were not destroyed
by falling because of gravity will be saved and added to the pool of options.

@@

Since there has to be a way to represent the struccture of a level in a a way that
both the algorithm as well as the game are able to interpret it \cite{togelius2016Representationsforsearch-basedmethods}, 
then the way to represent the elements of a member of the population in thos work 
is by using the id of each piece and the new added ones has a pointer to the respective data
that needs to be obtained, this way and individual can be represented as shown
on figure \ref{old_chrom} where each chromosome represents a certain item in the
pool of pieces, the numbers for this elements are assigned in a first come first
served basis, the numbers are infinitely incremented and the same pieces can be
repeated on each individual of the population.
